Ms 1

### 2017-10-16 ms1/ms1_display.Rmd
ms1 simplify

```{r dx_from_pde}
dx_from_pde = read_tsv('tables/dx_from_pde.tsv') %>% 
  spread(present, n) %>%
  mutate(pct=`TRUE`/(`TRUE` + `FALSE`)*100 %>% round(2)) %>%
  select(antibiotic, dx_cat, pct) %>%
  spread(dx_cat, pct) %T>%
  kable
```

>>>>

```{r dx_from_pde}
dx_from_pde = read_tsv('tables/dx_from_pde.tsv') %>% 
  spread(present, n) %>%
  mutate(pct=`TRUE`/(`TRUE` + `FALSE`)*100 %>% round(2)) %>%
  select(antibiotic, dx_cat, pct) %>%
  spread(dx_cat, pct)

dx_from_pde %>% kable
```
